---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
```

# Forecast Hub Autosubmission Framework

<!-- badges: start -->

```{r, results='asis'}
list.files("models") |>
  vapply(function(model) {
      glue::glue("![{model} status](https://github.com/covid19-forecast-hub-europe/covid19-forecast-hub-europe-submissions/workflows/{model}/badge.svg)") 
    },
    character(1)
  ) |>
  cat("\n")
```

<!-- badges: end -->

This repo contains the necessary infrastructure to handle automatic submissions
to a Forecast Hub (in this specific case, the [European Covid-19 Forecast
Hub](https://github.com/epiforecasts/covid19-forecast-hub-europe)).

Each model is stored as a git submodule (after a security scan) under the
`models/` folder and code is run automatically on a schedule via GitHub Actions.
The generated forecasts are then submitted to the hub repository as a pull
request.

```{r, message = FALSE}
nb_merged <- gh::gh(
  "/repos/{owner}/{repo}/pulls", 
  owner = "covid19-forecast-hub-europe", 
  repo = "covid19-forecast-hub-europe", 
  state = "closed", 
  .limit = Inf,
  .progress = FALSE
) |> 
  purrr::keep(~ .x$user$login == "epiforecasts-bot") |> 
  purrr::keep(~ !is.null(.x$merged_at)) |> 
  length()
```

As of `r Sys.Date()`, `r nb_merged` automated submissions have successfully been
merged.

## Guidelines for submitting your model

To submit your model for auto-submission, you need to [open an
issue](https://github.com/epiforecasts/covid19-forecast-hub-europe-submissions/issues/new?template=new-model.md)
providing:

-   The URL to a public git repository (e.g., hosted on GitHub) containing:
    -   a file `main.sh`, `main.R` or `main.py` **at its root**. This `main`
        file needs to create the forecasts with the expected folder structure in
        a folder named `data-processed`.
    -   a dependency management file. The exact name and syntax depend on the
        programming language you are using. Some examples are `requirements.txt`
        for python (with pip) or `renv.lock` for R (with renv). **All
        dependencies must have an exact version pinned to minimise risk of
        breakage with future dependency updates.**
-   the week day and time at which the workflow should run (as UTC).
-   the name of the GitHub user who should be tagged on pull request to review
    automated submissions.

Please note that although encouraged, it is not strictly mandatory to submit the
code generating your forecasts. You can submit a script fetching already
existing forecasts from another location such as an API, another GitHub
repository, a data repository, a dropbox folder, etc.


---

### Developer guidelines

Update submodules with

```
git submodule foreach git pull

```

Add a new submodule with

```
git submodule add <repo_url> models/repo_name
```

Remove a submodule with

```
git submodule deinit models/repo_name
git rm models/repo_name